A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-03-15 paper/paper.tex
updating framework fig
changes to intro and layout figure

\author{N. Neveu\footnotemark[7]\ \footnotemark[8]
  \and Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
  \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
  \and C. Bekas\footnotemark[3]
  \and A. Curioni\footnotemark[3]
  \and P. Arbenz\footnotemark[4]
}

@@

\begin{figure}[h!]
\begin{center}\normalsize
  \begin{tikzpicture}[text=black]%[scale=0.95, transform shape]
    \input{figures/opt-framework_code.tex}
  \end{tikzpicture}
\caption{Multi-objective framework: the pilot (master) solves the
optimization problem specified in the input file by coordinating optimizer
algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{center}
\end{figure}

@@

Here, we will focus on a real world application arising from PSI's
  \textsc{SwissFEL}~\cite{pedr:10} activities, which have an immediate and a
  long-range impact, by optimizing important parameters of PSI's \textsc{250
  MeV injector} test facility (and later for the full PSI \textsc{SwissFEL}).

>>>>

\author{N. Neveu\footnotemark[7]\ \footnotemark[8]
  \and Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
  \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
  \and P. Arbenz\footnotemark[4]
  \and C. Bekas\footnotemark[3]
  \and A. Curioni\footnotemark[3]
  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
  \and C. Kraus
}

@@

\begin{figure}[h!]
\begin{center}\normalsize

	\pgfdeclarelayer{background}
	\pgfsetlayers{background,main}
  \begin{tikzpicture}[text=black]%[scale=0.95, transform shape]
    \input{figures/opt-framework_code.tex}
  \end{tikzpicture}
\caption{Multi-objective framework: the pilot (master) solves the
optimization problem specified in the input file by coordinating optimizer
algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{center}
\end{figure}

@@

Here, we will focus on a real world applications arising from Paul Scherrer Institut's (PSI)
  \textsc{SwissFEL}~\cite{pedr:10} activities, and a high charge photoinjector 
  at the Argonne Wakefield Accelerator (AWA). Both of which have an immediate and a
  long-range impact, by optimizing important parameters for rf photoinjectors.
